---
title: "findings"
description: |
  A short description of the post.
author:
  - name: "Kay"
date: 02-19-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
```

Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill at <https://rstudio.github.io/distill>.

```{r}
#create_post("Conclusion")
```

Import data 
```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
library(dplyr)
```


Three-way Interaction of Condition, NFC, and Psychosocial Traits: 


```{r}
data$Condition <- as.factor(data$Condition)
```


MOd:ACE
```{r}
model1<-lm(Trauma_Knowledge~Condition+NFC+ACE+Condition*ACE+ACE*NFC+Condition*NFC+Condition*NFC*ACE, data)

```


```{r}
model2<-lm(DVS_state~Condition+NFC+ACE+Condition*ACE+ACE*NFC+Condition*NFC+Condition*NFC*ACE, data)

```


```{r}
model3<-lm(Empowerment_InternalTools~Condition+NFC+ACE+Condition*ACE+ACE*NFC+Condition*NFC+Condition*NFC*ACE, data)

```



```{r}
model4<-lm(Empowerment_Tradeoffs~Condition+NFC+ACE+Condition*ACE+ACE*NFC+Condition*NFC+Condition*NFC*ACE, data)


```


```{r}
model5<-lm(Empowerment_ExpectationSupport~Condition+NFC+ACE+Condition*ACE+ACE*NFC+Condition*NFC+Condition*NFC*ACE, data)

```



```{r}
model6<-lm(SelfCompassion~Condition+NFC+ACE+Condition*ACE+ACE*NFC+Condition*NFC+Condition*NFC*ACE, data)


```



```{r}
model7<-lm(In_GetBack~Condition+NFC+ACE+Condition*ACE+ACE*NFC+Condition*NFC+Condition*NFC*ACE, data)

```


```{r}
model8<-lm(In_End~Condition+NFC+ACE+Condition*ACE+ACE*NFC+Condition*NFC+Condition*NFC*ACE, data)

```

Create Table2

```{r}
library(stargazer)
```


```{r results = "asis"}
stargazer(model1, model2, model3, model4, model5, model6, model7, model8,
          
          title =  "Table 2. F and t-statistics of rational thinking and adverse childhood experience as the moderators.",
          df =F,
          dep.var.labels =c("Trauma knowledge", "Self-efficacy", "Internal tools", "Tradeoffs", "Social support", "Self-compassion", "Getting back intention", "Leaving intention"),
          covariate.labels = c("Constant",
                               "Condition", 
                               "NFC",
                               "ACE",
                          "Condition*ACE", 
                               "NFC*ACE",
                          "Condition*NFC",
                           "Condition*NFC*ACE"),
        
          
          type = "html", 
          align = TRUE, 
  
         
    
          intercept.bottom = F,
          intercept.top = T,
          digits = 2,
          model.names = T,
          single.row = T, out="Table2.html"
          )
```

No sig outcomes. No visualization is done. 

MOd:Fear
```{r}
model1<-lm(Trauma_Knowledge~Condition+NFC+Fear+Condition*Fear+Fear*NFC+Condition*NFC+Condition*NFC*Fear, data)

```


```{r}
model2<-lm(DVS_state~Condition+NFC+Fear+Condition*Fear+Fear*NFC+Condition*NFC+Condition*NFC*Fear, data)

```


```{r}
model3<-lm(Empowerment_InternalTools~Condition+NFC+Fear+Condition*Fear+Fear*NFC+Condition*NFC+Condition*NFC*Fear, data)

```



```{r}
model4<-lm(Empowerment_Tradeoffs~Condition+NFC+Fear+Condition*Fear+Fear*NFC+Condition*NFC+Condition*NFC*Fear, data)


```


```{r}
model5<-lm(Empowerment_ExpectationSupport~Condition+NFC+Fear+Condition*Fear+Fear*NFC+Condition*NFC+Condition*NFC*Fear, data)

```



```{r}
model6<-lm(SelfCompassion~Condition+NFC+Fear+Condition*Fear+Fear*NFC+Condition*NFC+Condition*NFC*Fear, data)


```



```{r}
model7<-lm(In_GetBack~Condition+NFC+Fear+Condition*Fear+Fear*NFC+Condition*NFC+Condition*NFC*Fear, data)
```


```{r}
model8<-lm(In_End~Condition+NFC+Fear+Condition*Fear+Fear*NFC+Condition*NFC+Condition*NFC*Fear, data)
```

Create table 

```{r}
stargazer(model1, model2, model3, model4, model5, model6, model7, model8,
          
          title =  "Table 3. F and t-statistics of rational thinking and fear of the current partner as the moderators.",
          df =F,
          dep.var.labels =c("Trauma knowledge", "Self-efficacy", "Internal tools", "Tradeoffs", "Social support", "Self-compassion", "Getting back intention", "Leaving intention"),
          covariate.labels = c("Constant",
                               "Condition", 
                               "NFC",
                               "Fear",
                          "Condition*Fear", 
                               "NFC*Fear",
                          "Condition*NFC",
                           "Condition*NFC*Fear"),
        
          
          type = "html", 
          align = TRUE, 
  
         
    
          intercept.bottom = F,
          intercept.top = T,
          digits = 2,
          model.names = T,
          single.row = T, out="Table3.html"
          )
```

The interaction effect is sig. on internal tools and will be visualized. 

Plot1: ConditionxNFCXFear-> Self-efficacy

```{r}
newdata<-select(data, c("Fear", "NFC", "Condition", "DVS_state"))

```

```{r}
newdata<-na.omit(newdata)
```


```{r}
newdata$Fear <- cut(newdata$Fear, breaks=c(0, 1.17, 6), include.lowest= TRUE)
```


```{r}
levels(newdata$Fear)
```



```{r}
newdata$Condition <- factor(newdata$Condition,
levels = c(0,1),
labels = c("Control" , "Treatment"))
```


```{r}

newdata$Fear <- factor(newdata$Fear,
levels = c("[0,1.17]", "(1.17,6]"),
labels = c("Less than 1.17", "More than 1.17"))


plot1<-ggplot(newdata, aes(x  = NFC, y = DVS_state))+
  geom_smooth(aes(linetype = Condition), method = "lm", color = "black")+
  facet_wrap(~Fear, ncol = 2)+
  theme_minimal()+
  labs(x =  "Rational thinking", y = "Self-efficacy", subtitle = "Fear of the current partner")
```


```{r}
plot1
```


Mod: BPD 

```{r}
model1<-lm(Trauma_Knowledge~Condition+NFC+BPD+Condition*BPD+BPD*NFC+Condition*NFC+Condition*NFC*BPD, data)

```


```{r}
model2<-lm(DVS_state~Condition+NFC+BPD+Condition*BPD+BPD*NFC+Condition*NFC+Condition*NFC*BPD, data)


```


```{r}
model3<-lm(Empowerment_InternalTools~Condition+NFC+BPD+Condition*BPD+BPD*NFC+Condition*NFC+Condition*NFC*BPD, data)


```



```{r}
model4<-lm(Empowerment_Tradeoffs~Condition+NFC+BPD+Condition*BPD+BPD*NFC+Condition*NFC+Condition*NFC*BPD, data)



```


```{r}
model5<-lm(Empowerment_ExpectationSupport~Condition+NFC+BPD+Condition*BPD+BPD*NFC+Condition*NFC+Condition*NFC*BPD, data)


```



```{r}
model6<-lm(SelfCompassion~Condition+NFC+BPD+Condition*BPD+BPD*NFC+Condition*NFC+Condition*NFC*BPD, data)



```



```{r}
model7<-lm(In_GetBack~Condition+NFC+BPD+Condition*BPD+BPD*NFC+Condition*NFC+Condition*NFC*BPD, data)

```


```{r}
model8<-lm(In_End~Condition+NFC+BPD+Condition*BPD+BPD*NFC+Condition*NFC+Condition*NFC*BPD, data)

```


Crete table 4


```{r}
stargazer(model1, model2, model3, model4, model5, model6, model7, model8,
          
          title =  "Table 4. F and t-statistics of rational thinking and borderline personality traits as the moderators.",
          df =F,
          dep.var.labels =c("Trauma knowledge", "Self-efficacy", "Internal tools", "Tradeoffs", "Social support", "Self-compassion", "Getting back intention", "Leaving intention"),
          covariate.labels = c("Constant",
                               "Condition", 
                               "NFC",
                               "BPD",
                          "Condition*BPD", 
                               "NFC*BPD",
                          "Condition*NFC",
                           "Condition*NFC*BPD"),
        
          
          type = "html", 
          align = TRUE, 
  
         
    
          intercept.bottom = F,
          intercept.top = T,
          digits = 2,
          model.names = T,
          single.row = T, out="Table4.html"
          )
```


No significant interaction and thus no visualization is needed. 

Mod: mom avoidance 

```{r}
model1<-lm(Trauma_Knowledge~Condition+NFC+Mom_avoidance+Condition*Mom_avoidance+Mom_avoidance*NFC+Condition*NFC+Condition*NFC*Mom_avoidance, data)

```


```{r}
model2<-lm(DVS_state~Condition+NFC+Mom_avoidance+Condition*Mom_avoidance+Mom_avoidance*NFC+Condition*NFC+Condition*NFC*Mom_avoidance, data)
```


```{r}
model3<-lm(Empowerment_InternalTools~Condition+NFC+Mom_avoidance+Condition*Mom_avoidance+Mom_avoidance*NFC+Condition*NFC+Condition*NFC*Mom_avoidance, data)
```



```{r}
model4<-lm(Empowerment_Tradeoffs~Condition+NFC+Mom_avoidance+Condition*Mom_avoidance+Mom_avoidance*NFC+Condition*NFC+Condition*NFC*Mom_avoidance, data)


```


```{r}
model5<-lm(Empowerment_ExpectationSupport~Condition+NFC+Mom_avoidance+Condition*Mom_avoidance+Mom_avoidance*NFC+Condition*NFC+Condition*NFC*Mom_avoidance, data)

```



```{r}
model6<-lm(SelfCompassion~Condition+NFC+Mom_avoidance+Condition*Mom_avoidance+Mom_avoidance*NFC+Condition*NFC+Condition*NFC*Mom_avoidance, data)


```



```{r}
model7<-lm(In_GetBack~Condition+NFC+Mom_avoidance+Condition*Mom_avoidance+Mom_avoidance*NFC+Condition*NFC+Condition*NFC*Mom_avoidance, data)
```


```{r}
model8<-lm(In_End~Condition+NFC+Mom_avoidance+Condition*Mom_avoidance+Mom_avoidance*NFC+Condition*NFC+Condition*NFC*Mom_avoidance, data)


```



Create Table 

```{r}
stargazer(model1, model2, model3, model4, model5, model6, model7, model8,
          
          title =  "Table 5. F and t-statistics of rational thinking and avoidance attachment to a mother figure as the moderators.",
          df =F,
          dep.var.labels =c("Trauma knowledge", "Self-efficacy", "Internal tools", "Tradeoffs", "Social support", "Self-compassion", "Getting back intention", "Leaving intention"),
          covariate.labels = c("Constant",
                               "Condition", 
                               "NFC",
                               "Avoidance",
                          "Condition*Avoidance", 
                               "NFC*Avoidance",
                          "Condition*NFC",
                           "Condition*NFC*Avoidance"),
        
          
          type = "html", 
          align = TRUE, 
  
         
    
          intercept.bottom = F,
          intercept.top = T,
          digits = 2,
          model.names = T,
          single.row = T, out="Table5.html"
          )
```

The effects on leaving intention is significant Plot2: ConditionxNFCxMom avoidance -> Leaving intention  



```{r}
newdata<-select(data, c("Mom_avoidance", "NFC", "Condition", "In_End"))

```


```{r}
#Indicate JN from SPSS 
newdata$Mom_avoidance <- cut(newdata$Mom_avoidance, breaks=c(0, 2.88, 5), include.lowest= TRUE)
```

```{r}
levels(newdata$Mom_avoidance)
```



```{r}
newdata$Condition <- factor(newdata$Condition,
levels = c(0,1),
labels = c("Control" , "Treatment"))
```

```{r}
newdata<-na.omit(newdata)
```



```{r}

newdata$Mom_avoidance <- factor(newdata$Mom_avoidance,
levels = c("[0,2.88]", "(2.88,5]"),
labels = c("Less than 2.88", "More than 2.88"))


plot2<-ggplot(newdata, aes(x  = NFC, y = In_End))+
  geom_smooth(aes(linetype = Condition), method = "lm", color = "black")+
  facet_wrap(~Mom_avoidance, ncol = 2)+
  theme_minimal()+
  labs(x =  "Rational thinking", y = "Intention to end the relationship", subtitle = "Avoidance of a mother figure")

```


```{r}
plot2
```


Try create another version of the model plot using geom_point


```{r}
ggplot(newdata, aes(x= NFC, y = In_End))+
  geom_point(aes(color = Condition))+
  facet_wrap(~Mom_avoidance)+
  geom_smooth(aes(color = Condition))
               
  
```


```{r}
#install.packages("interactions")
```
```{r}
library(interactions)
```


```{r}
interact_plot(model8, pred = NFC, modx = Condition, mod2 = Mom_avoidance, linearity.check = TRUE, plot.points = 2)
```

```{r}
model8.1 <- lm(In_End~Condition*poly(NFC,2)*Mom_avoidance, data)
summary(model8.1)
#Not significant .. so use the linear?
```


Uncertainty: visualize the standard errors 
```{r}
un_model8<-broom::tidy(model8, conf.int = TRUE)
un_model8
```



```{r}
ggplot(un_model8, aes(term, estimate))+
  geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2)+
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high))+
  geom_point()+
  coord_flip()
```



