---
title: "Research background"
description: |
  A short description of the post.
author:
  - name: 'fatal: unable to access ''C:/Users/KKari/OneDrive/??????/.config/git/config'':
      Invalid argument'
date: 02-19-2021
output:
  distill::distill_article:
    self_contained: false
---



```{r}
summary(data)
```

Check outlier
```{r}
 mahal <- mahalanobis(data[ , -c(18:30)],
                      colMeans(data[ ,-c(18:30)], na.rm = TRUE), 
                      cov(data[ , -c(18:30)], 
                          use = "pairwise.complete.obs"))
                                                                        

```


```{r}
cutoff = qchisq(.999, ncol(data[, -c(18:30)]))
```


```{r}
summary(mahal<cutoff)
```


```{r}
correlation = cor(data[ ,-c(18:30)], use = "pairwise.complete.obs")
```

```{r}
symnum(correlation)
```

Assumption check 


Create a new data frame without variables with missing values as I assumed, chi square distribution function in R does not support NA. Or it may but I just dont know yet 


```{r}
dataII <- data %>% select(ACE:SelfCompassion)
```


```{r}

random = rchisq(nrow(data[ ,-c(18:30)]), 7)
```

```{r}
fake = lm(random~.,na.rm = TRUE, data=data[ ,-c(18:30)])
```

Create standardized residuals 

1. Linearity check
```{r}
standardized_residuals= rstudent(fake)
qqnorm(standardized_residuals)
abline(0,1)

```

2. Normality check 

```{r}
hist(standardized_residuals)
```

3. . Error homogeneity (shold be around and eqaual along the fitted values) and 4. independce of errors (should look random) 
fitted values refer to predicted scores of the data set 
```{r}
fitted = scale(fake$fitted.values)
plot(fitted, standardized_residuals)
abline(0,0)
abline(v = 0)
```




